VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-19 snapshot_system/paper_abs.tex
re

\begin{abstract}
Data deduplication has been widely used for cloud data backup
because of excessive redundant content blocks. Common techniques 
perform fingerprint comparison to remove duplicates
across virtual machines.
However, letting a duplicate data block be shared
by many virtual machines represents a tradeoff between
storage efficiency and data availability.
%by many virtual machines creates data dependence and is less fault-resilient. 
%%This paper studies the impact of deduplication on 
%%fault resilidence  of virtual machine snapshots, created by data dependence  among duplicates
%%and proposes a VM-centric approach that strikes a balance between deduplication efficiency
%%and fault isolation 
This paper proposes a VM-centric backup service on a converged  cloud cluster architecture
and  strikes a tradeoff for better fault isolation with competitive  deduplication efficiency.
It localizes deduplication as much as possible within each 
virtual machine, guided by similarity
search, and it restricts global deduplication under popular chunks with extra replication support.
It associates  underlying file blocks with one VM for most cases
and proposes an approximate method for fast and simplified snapshot deletion.
This VM-centric scheme also has  an advantage of   using less  computing resources, suitable for running
the backup service on a converged cloud architecture that cohosts  many other services.
This  paper  describes an evaluation of this scheme to assess  its deduplication 
efficiency and fault resilience.

>>>>

\begin{abstract}
Data deduplication is important  for snapshot backup of virtual machines (VMs)
because of excessive redundant content.  Fingerprint search for source-side duplicate 
detection is resource intensive when the backup service for VMs  is co-located with  other 
cloud services.  This paper proposes a VM-centric backup service with  a tradeoff 
for a competitive  deduplication efficiency while using small computing resources, 
suitable for running on a converged cloud architecture that cohosts  many other services.
The key techniques in the proposed scheme are to localize deduplication as much as 
possible within each VM guided by similarity search, restrict global 
deduplication under popular chunks with extra replication support,
and use an approximate method for fast and simplified snapshot deletion.
This VM-centric design also improves the snapshot availability  during machine failures  
by separating popular chunks and associating  file system blocks with one VM for non-popular chunks.
This  paper  describes an evaluation of this VM-centric scheme to assess  its deduplication 
efficiency, resource usage,  and fault tolerance.
